\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts


\title{Church Research Concept}
\author{MUBIRU GRACE
215004794
15/U/7729/PS}
\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
\section{Concept}
Worship is a part of almost everyone today. people go to worship places with expectations which they think those respective churches are able to fulfill.
for that reason, some people are specific in nature about the kind of churches they attend to. 
some are fully attached to their born religions and so they always  look for a church with the same beliefs, 
Others can go to church depending on its vicinity, 
there are those are attracted to church just by the nature of the building.
There is also another category of people who go to a certain church because of the leader of that particular church.
\\   
{  On top of that, different religious leaders need to identify where they need new churches to be established, For-example according to this research, you will notice that there is only one SDA Adventist Church in Kyengera, two Catholic churches and  two for the Anglicans competing with the many churches of Born-again pentecostal churches. This research can awaken respective religious leaders to do something about the situation.}
\\   
For those reasons, I came up with church research as a topic trying to identify and help whoever person wants a church in Kyengera area, trying to cover up all the factors a person may consider to choose a church.


\subsection{Explanation of the research topic}
The ODK build form has five columns with each column representing a unique attribute of the church.
\subsubsection{id}
This section identifies the unique number of the church. it serves a the primary key

\subsubsection{Name}
This contains the name of the church. It is so interesting that someone can choose one church over the other just because of the name. So this research will help such people depending on the name. Someone may choose to go to St. Kizito simply because they share a name

\subsubsection{GPSLocation}
This is one of the most important columns. It shows the geographical location of the church. This enables one to see how far the church is from their residence and they decide accordingly. The coordinates are taken automatically using GPS.
\subsubsection{Image}
Under this column, you will find the actual structural view of each church. Taken by the Samsung Galaxy Note 4 full HD camera, the image depicts the actual structure of the church. And a person who goes to church because of the structure, has a chance of making a clear decision.
\subsubsection{Description}
This is a column where you will find whatever you couldn't find from other columns. It will peharps  be a center of decision to either go to that church or another.
\section{Conclusion}
We cannot get away with the fact that churches are part of our daily life. But the church you go to always make you feel in a certain way. So you cannot just go to any church. Someone needs a church where they go and feel at home, have their spirits fed and experience a positive impact on their lives.
\end{document}  